%% -*- coding: euc-jp -*-
%% 参考文献
\begin{thebibliography}{99}
 \bibitem{ADVENTURE}
         ADVENTURE Project. \\
         \url{http://adventure.sys.t.u-tokyo.ac.jp/}
 \bibitem{Boeing787}
         Boeing 787 Dreamliner. \\
         \url{http://www.boeing.com/commercial/787family/}
 \bibitem{Davis2006}
         {\sc Davis, T. A.}
         {\it Direct Methods for Sparse Linear Systems}.
         Society for Industrial and Applied Mathematics, 2006.
 \bibitem{Farhat1991}
         {\sc Farhat, C. and Roux, F.-X.}
         A method of finite element tearing and interconnecting
         and its parallel solution algorithm.
         {\it International Journal for Numerical Methods in Engineering},
         vol.~32, issue~6, pp.~1205--1227, 1991.
 \bibitem{Fish1992}
         {\sc Fish, J.}
         The s-version of the finite element method.
         {\it Computers and Structures},
         vol.~43, issue~3, pp.~539--547, 1992.
 \bibitem{Intel_Compilers}
         Intel Compilers from Intel. \\
         \url{http://software.intel.com/en-us/articles/intel-compilers/}
 \bibitem{Kawai2006}
         {\sc Kawai, H.}
         ADVENTURE AutoGL:~a handy graphics and GUI library
         for researchers and developers of numerical simulations.
         {\it Computer Modeling in Engineering and Sciences},
         vol.~11, issue~3, pp.~111--120, 2006.
 \bibitem{Kelley2003}
         {\sc Kelley, C. T.}
         {\it Solving Nonlinear Equations with Newton's Method}.
         Society for Industrial and Applied Mathematics, 2003.
 \bibitem{Kikuchi2008}
         {\sc Kikuchi, M., Wada, Y., Takahashi, M. and Li, Y.}
         Fatigue crack growth simulation using s-version FEM.\
         {\it Advanced Materials Research},
         vols.~33--37, pp.~133--138, 2008.
 \bibitem{Mandel1993}
         {\sc Mandel, J.}
         Balancing domain decomposition.
         {\it Communications in Numerical Methods in Engineering},
         vol.~9, issue~3, pp.~233--241, 1993.
 \bibitem{Intel_MKL}
         Math Kernel Library from Intel. \\
         \url{http://software.intel.com/en-us/articles/intel-mkl/}
 \bibitem{Matthies2003}
         {\sc Matthies, H. and Steindorf, J.}
         Partitioned strong coupling algorithms
         for fluid--structure interaction.
         {\it Computers and Structures},
         vol.~81, pp.~805--812, 2003.
 \bibitem{Minami2010}
         {\sc Minami, S. and Yoshimura, S.}
         Performance evaluation of nonlinear algorithms with line-search
         for partitioned coupling techniques for fluid--structure interactions.
         {\it International Journal for Numerical Methods in Fluids},
         vol.~64, issues~10--12, pp.~1129--1147, 2010.
 \bibitem{Nagashima2003}
         {\sc Nagashima, T., Omoto, Y. and Tani, S.}
         Stress intensity factor analysis of interface cracks using X-FEM.\
         {\it International Journal for Numerical Methods in Engineering},
         vol.~56, issue~8, pp.~1151--1173, 2003.
 \bibitem{Nishikawa2007}
         {\sc Nishikawa, H., Serizawa, H. and Murakawa, H.}
         Actual application of FEM to analysis
         of large scale mechanical problems in welding.
         {\it Science and Technology of Welding and Joining},
         vol.~12, issue~2, pp.~147--152, 2007.
 \bibitem{Nishioka1983}
         {\sc Nishioka, T. and Atluri, S. N.}
         Analytical solution for embedded elliptical cracks,
         and finite element alternating method
         for elliptical surface cracks, subjected to arbitrary loadings.
         {\it Engineering Fracture Mechanics},
         vol.~17, issue~3, pp.~247--268, 1983.
 \bibitem{Ogino2005}
         {\sc Ogino, M., Shioya, R., Kawai, H. and Yoshimura, S.}
         Seismic response analysis of nuclear pressure vessel model
         with ADVENTURE system on the Earth Simulator.
         {\it Journal of the Earth Simulator},
         vol.~2, pp.~41--54, 2005.
 \bibitem{Okada2005}
         {\sc Okada, H. and Kamibeppu, T.}
         A virtual crack closure-integral method (VCCM)
         for three-dimensional crack problems
         using linear tetrahedral finite elements.
         {\it International Journal for Computational Methods
         in Engineering Science and Mechanics},
         vol.~10, issue~3, pp.~229--238, 2005.
 \bibitem{Okada2008}
         {\sc Okada, H., Kawai, H. and Araki, K.}
         A virtual crack closure-integral method (VCCM)
         to compute the energy release rates and stress intensity factors
         based on quadratic tetrahedral finite elements.
         {\it Engineering Fracture Mechanics},
         vol.~75, issue~15, pp.~4466--4485, 2008.
 \bibitem{Saad2003}
         {\sc Saad, Y.}
         {\em Iterative Methods for Sparse Linear Systems, Second Edition}.
         Society for Industrial and Applied Mathematics, 2003.
 \bibitem{Schenka2001}
         {\sc Schenka, O., G\"artnerb, K., Fichtnera, W. and Strickera, A.}
         PARDISO:~a high-performance serial and parallel sparse linear solver
         in semiconductor device simulation.
         {\it Future Generation Computer Systems},
         vol.~18, issue~1, pp.~69--78, 2001.
 \bibitem{Sugimoto2010}
         {\sc Sugimoto, S., Margron, V. and Yoshimura, S.}
         Parallel vibration analysis of magnetic--structural coupled phenomena
         of MRI model.
         In {\it Proceedings
         of the 9th World Congress on Computational Mechanics
         and the 4th Asian Pacific Congress on Computational Mechanics},
         Sydney, Australia, July 2010.
 \bibitem{Terada2001}
         {\sc Terada, K. and Kikuchi, N.}
         A class of general algorithms for multi-scale analyses
         of heterogeneous media.
         {\it Computer Methods in Applied Mechanics and Engineering},
         vol.~190, issues~40--41, pp.~5427--5464, 2001.
 \bibitem{Tezduyar2007}
         {\sc Tezduyar, T. E. and Sathe, S.}
         Modelling of fluid--structure interactions
         with the space--time finite elements: solution techniques.
         {\it International Journal for Numerical Methods in Fluids},
         vol.~54, issues~6--8, pp.~855--900, 2007.
 \bibitem{Yagawa1991}
         {\sc Yagawa, G., Soneda, N. and Yoshimura, S.}
         A large scale finite element analysis
         using domain decomposition method on a parallel computer.
         {\it Computers and Structures},
         vol.~38, issues~5--6, pp.~615--625, 1991.
 \bibitem{Yagawa1993}
         {\sc Yagawa, G., Yoshioka, A., Yoshimura, S. and Soneda, N.}
         A parallel finite element method with a supercomputer network.
         {\it Computers and Structures},
         vol.~47, issue~3, pp.~407--418, 1993.
 \bibitem{Yagawa1993_2}
         {\sc Yagawa, G. and Shioya, R.}
         Parallel finite elements on a massively parallel computer
         with domain decomposition.
         {\it Computing Systems in Engineering},
         vol.~4, issues~4--6, pp.~495--503, 1993.
 \bibitem{Yamada2011}
         {\sc Yamada, Takahiro.}
         Finite element procedure for overlapping meshes
         based on domain decomposition approach using background voxel mesh.
         In {\it Proceedings of the 11th US National Congress
         on Computational Mechanics},
         213901, Minneapolis, MN, USA, July 2011.
 \bibitem{Yamada2008}
         {\sc Yamada, Tomonori and Yoshimura, S.}
         Line search partitioned approach
         for fluid--structure interaction analysis of flapping wing.
         {\it Computer Modeling in Engineering and Sciences},
         vol.~24, issue~1, pp.~51--60, 2008.
 \bibitem{Yoshimura2002}
         {\sc Yoshimura, S., Shioya, R., Noguchi, H. and Miyamura, T.}
         Advanced general-purpose computational mechanics system
         for large-scale analysis and design.
         {\it Journal of Computational and Applied Mathematics},
         vol.~149, issue~1, pp.~279--296, 2002.
 \bibitem{Zhang2001}
         {\sc Zhang, Q. and Hisada, T.}
         Analysis of fluid--structure interaction problems
         with structural buckling and large domain changes
         by ALE finite element method.
         {\it Computer Methods in Applied Mechanics and Engineering},
         vol.~190, issue~48, pp.~6341--6357, 2001.
 \bibitem{Oguni1991}
         {\sc 小国力 編著, 村田健郎, 三好俊郎, Dongarra, J. J., 長谷川秀彦 著.}
         行列計算ソフトウェア---WS、スーパーコン、並列計算機.
         丸善, 1991.
 \bibitem{shippai}
         失敗知識データベース. \\
         \url{http://www.sozogaku.com/fkd/}
 \bibitem{Shiratori1980}
         白鳥正樹, 三好俊郎, 松下久雄 共著.
         数値破壊力学.
         実教出版, 1980.
 \bibitem{Suzuki1999}
         鈴木克幸, 大坪英臣, 閔勝載, 白石卓士郎.
         重合メッシュ法による船体構造のマルチスケール解析.
         {\it Transactions of the Japan Society
         for Computational Engineering and Science},
         vol.~1999, 19990020, 1999.
 \bibitem{Suzuki2002}
         鈴木克幸, 大坪英臣, 中住昭吾, 榛村太亮.
         重合メッシュ法におけるグローバル・ローカル反復解析.
         日本造船学会論文集,
         vol.~192, pp.~691--696, 2002.
 \bibitem{jsmecode}
         日本機械学会.
         発電用原子力設備規格維持規格 (JSME S NA1-2004),
         2004.
 \bibitem{Yagawa1988}
         矢川元基 編.
         破壊力学---理論・解析から工学的応用まで.
         培風館, 1998.
\end{thebibliography}
